I can see clearly now: reinterpreting statistical significance

### 2019-01-07 rebuttal.md

_I agree that a downside of hypothesis testing is often (wrongly) seen as an end in itself, rather than the scientific knowledge that is gained from the test. However, I am not convinced that your suggestion will solve this. Here are my thoughts:_

Thanks for your perspective. We are also not convinced our suggestion will solve this major problem, to put it mildly. But we are hoping it will help (and think that in small ways it already has). We respond to your specific points below.

_2. I don’t understand the logic that using the term ‘clear’ automatically makes the need for effect sizes and confidence intervals more obvious. Can you explain this logical jump more fully within the manuscript?_

We don't argue that it's automatic, but we do rely on the assumption that use of a term whose colloquial meaning closely matches what P values indicate will lead to clearer communication. We gave an example where we believe the word "clear" underlines the absence of effect sizes (L136 of ORIGINAL), and mentioned CIs in the table. We have now added another mention to the table, and an UNCONVINCING comment to the ¶ where we present the table.

@@

_3. If some people adopt this terminology, whilst others do not, it could become a very confusing and unclear landscape of scientific understanding. I think this would have more strength if a single domain or several journals gave new guidelines to only use this term, however that would likely require a more evidence-based case than presented here._

We agree about strength, and hope to head in this direction. Publishing the idea is, we hope, a first step. We have found through informal discussion that there is little confusion when the idea of clarity is combined with reference to P values or confidence intervals. We have made this point more explicit in the MS.

### 2019-01-07 doc.tex
First pass at revisions and rebuttal

The value of NHST is that asking whether we can reject the null hypothesis is a proxy for asking whether we clearly \emph{how} our data differs from it. For example, in a t-test, we are nominally asking whether we can see a \emph{difference} between two means, but the scientific question is whether we a confident which of the two means is \emph{larger}; similarly, tests for whether two values are correlated are a proxy for whether we can see the sign of the correlation coefficient \citep{robinson2001past}. In other cases (e.g., a one-way ANOVA), it may not be simple to describe the difference we see, but NHST is still a reasonable, accepted way to evaluate whether an effect has been seen clearly.

@@

Descriptions of statistical results using the language of clarity should begin with reference to the effect. For example, ``The difference between the control and treatment group was not statistically clear.'' Table~\ref{quotetab} shows published examples of statements that misinterpret \pvals in three different ways and demonstrates how to rephrase them in the language of clarity. We have attempted to do this thoughtfully, and therefore the language on the right differs from the language on the left in many ways. The point is not that changing ``significance'' to ``clarity'' is a substantial improvement by itself, but that it can prompt rethinking and reinterpretation.

@@

The use of statistical clarity could be confounded with other meanings of the word clarity. We have found that scientists' understand of our proposed use of statistical clarity is enhanced by connecting clarity statments to statements about P values.

ADD a bit about winners' curses, plausibility and the like here (and take some of it out of the Conclusions.

>>>>

The value of NHST is that asking whether we can reject the null hypothesis is a proxy for asking whether we see clearly \emph{how} our data differs from it. For example, in a t-test, we are nominally asking whether we can see a \emph{difference} between two means, but the scientific question is whether we are confident which of the two means is \emph{larger}; similarly, tests for whether two values are correlated are a proxy for whether we are confident about the \emph{sign} of the correlation coefficient \citep{robinson2001past}. In other cases (e.g., a one-way ANOVA), it may not be simple to describe the difference we see, but NHST is still a reasonable, widely accepted way to evaluate whether an effect has been seen clearly.

@@

Descriptions of statistical results using the language of clarity should begin with reference to the effect. For example, ``The difference between the control and treatment group was not statistically clear.'' Table~\ref{quotetab} shows published examples of statements that misinterpret \pvals in three different ways and demonstrates how to rephrase them in the language of clarity. We have attempted to do this thoughtfully, and therefore the language on the right differs from the language on the left in many ways. The point is not that changing ``significance'' to ``clarity'' is a substantial improvement by itself, but that it can prompt rethinking and reinterpretation. We also hope that, by drawing attention to effects, the language of clarity will encourage more reporting of effect sizes and confidence intervals.

@@

The use of statistical clarity could be confounded with other meanings of the word clarity. We have found that scientists' understanding of our proposed use of statistical clarity is enhanced by explicitly connecting clarity statments to statements about P values.

ADD a bit about winners' curses, plausibility and the like here (and take some of it out of the Conclusions. Should we say specifically that we are agnostic about (supportive of?) the idea that NHST and/or frequentist stats are overused?
